Appendix 1: Preregistered analysis with simulated data

### 2025-05-30 preregistration_code.Rmd
Applying additional cleaning

#afterdata changing negative blood donation history to missing data for bd04 from 3 participants
data %>% filter(bd04 < 0)
data <- data %>% 
  mutate(bd04 = ifelse(bd04 < 0, NA, bd04))

@@

#afterdata adding additional exclusion criteria in line with preregistered exclusion for bd02 & bd03

@@

@@

#afterdata adding in additional exclusion criteria for bd02 & bd03
data <- data %>% 
  filter(bd02 >= 1)

@@

@@

```{r}
#afterdata model comparison won't run because no participants responded with "1" for ai01 ("I am intimately familiar with what is going on with regard to donating blood")

data.fit2 <- data.fit2 %>%
  mutate(
    ai01 = as.numeric(as.character(ai01)),  # convert to numeric if factor
    ai01 = ai01 - 1,                         # subtract 1 so lowest category is now 1
    #ai01 = factor(ai01, ordered = TRUE)      # convert back to ordered factor
  )
table(data.fit$ai01)

@@

```{r}
knitr::knit_exit()
#Stop here with real data and review results before modelling.
```

>>>>

```{r}
data %>% filter(bd04 < 0)
data %>% filter(bd03 > 12)

data <- data %>% 
  mutate(
    bd04 = ifelse(bd04 < 0, NA, bd04)/7,
    bd03 = ifelse(bd03 > 12, NA, bd03)
)

#afterdata changing negative blood donation history to missing data for bd04 from 3 participants
#afterdata changing values over 12 (maximum number of whole blood donations for men within 2 years) for bd03 to missing.
#afterdata rescaling bd04 to number of weeks since last donation
```

@@

@@

#afterdata adding additional exclusion criteria in line with preregistered exclusion for bd02 & bd03  
```

@@

data <- data %>% 
  filter(bd02 >= 1)

@@

#afterdata adding in additional exclusion criteria for bd02 & bd03
```

@@

data.fit2 <- data.fit2 %>%
  mutate(
    ai01 = as.numeric(as.character(ai01)),  # convert to numeric if factor
    #ai01 = ai01 - 1,                         # subtract 1 so lowest category is now 1
    #ai01 = factor(ai01, ordered = TRUE)      # convert back to ordered factor
  )
table(data.fit$ai01)

#afterdata model comparison won't run because no participants responded with "1" for ai01 ("I am intimately familiar with what is going on with regard to donating blood")
  #I'm not sure why but if you just specify that ai01 is numeric it runs without needed to merge level 1 and 2. 
```

@@

```{r}
#knitr::knit_exit()
#Stop here with real data and review results before modelling.
```
